Data Analytics Introduction Using Python Training

### 2024-11-08 MsaPythonDataAnalytics.qmd
content day 1

---
title: "Data Analytics Introduction Using Python Training"
jupyter: python3
format: 
  revealjs:
    theme: serif
    smaller: false
    scrollable: true
code-fold: true
---

@@

## Python Interface

@@

Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

@@

1 + 1
```

@@

NumPy, short for Numerical Python, is one of the most important foundational packages for numerical computing in Python. Numpy works with array from 1-n dimenisional.

>>>>

---
title: "Data Analytics Introduction Using Python Training"
jupyter: python3
format: 
  revealjs:
    theme: serif
    smaller: true
    scrollable: true
code-fold: true
---

@@

## Python Interface {.smaller}

@@

::: {.panel-tabset}

### IDE's Common to Python

- Pycharm
- Spyder
- vsCode
- Rstudio
- Positron (*New in Beta*)
- Text editors
  - notepad ++
  - vim
  - sublime
- e.t.c

Though there are many and the tool of choice is open for use, for now we can focus on using vsCode as this is universal to also other programming languages but if you are interested in a polygot system you can test positron.

### Installations

***Let us check what installations you have***

- Python Installation
- IDE Installation
- To install all this together we prefer [anaconda](www.anaconda.com)
  - Anaconda | **full suit of packages and tools**
  - miniconda | **minimal and necessary packages**

## Python | Hello World

Python being an interpreted high level programming language, making things easier for the programmer. Able to pick up the things very easily.

Let us start with the first code.

::: {.panel-tabset}

### Hello World

```{python}
#| echo: True

print("Hello WOrld")

Let us use it as a calculator.

```{python code-line-numbers="4,6,8,10"}
#| echo: true
#| eval: false

2 + 2  #Add
#4
3 - 1  #Subtract
#2
4 * 5  #Multiply
#20
20 / 5 #Divide
#4 
5 ** 2 #Exponent
#25
5 % 2  #?What is the result

Using it as an ***input***

```{python}
#| echo: true
#| eval: false

input("What's your name")

Using ***comments***

@@

#This is a comment

### Data types

**Strings**

```{python}
#| echo: true
first_string = "My first String"
first_string
```

***List***

```{python}
#| echo: true
first_list = [1,2,3,4]
first_list
```

***Tuples***
```{python}
#| echo: true
first_tuple = (1,2,3)
first_tuple
```

***Dictionary***
```{python}
#| echo: true
first_dic = {'a' : [1,2,3], 'b' : [4,5,6], 'c' : [7,6,8]}
first_dic
```

### Methods & Functions

**Methods**

Method: Attributes associated to different objects and data types. As well classes at a broader level

```{python}
#| echo: true
first_string.upper()
first_string.lower()
first_string.swapcase()
first_string.rsplit() #separating or delimiter is a space

***Functions***

```{python}
#| echo: true
first_list = [1,2,3,4]
first_list
```

### Summary Sheets

|**Operator**|**Description**|**Associativity**|
|----|-----|------|
|`{key:expr,...}`   |Dictionary creation| NA|
|`{ expr ,...}`     |Set creation       | NA|
|`[ expr ,...]`     |List creation      | NA|
|`( expr ,...)`     |Tuple creation or just parentheses      | NA|
|`f ( expr ,...)`     |Function call      | L|
|`x [ index : index ]`     |Slicing      | L|
|`x [ index ]`     |Indexing      | L|
|`x . attr`     |Attribute reference      | L|
|`x ** y`     |Exponentiation (x to the yth power)      | R|
|`~ x`     |Bitwise NOT      | NA|
|`+x, -x`     |Unary plus and minus      | NA|
|`x*y, x/y, x//y, x%y`     |Multiplication, division, truncating division,remainder      | L|
|`x+y, x-y` | Addition, subtraction | L |
|`x<<y, x>>y` | Left-shift, right-shift | L |
|`x & y` | Bitwise AND | L |
|`x ^ y` | Bitwise XOR | L |
|`x | y` | Bitwise OR | L |
|`x<y, x<=y, x>y, x>=y, x<>y (v2 only),x!=y, x==y` | Comparisons (less than, less than or equal, greater than, greater than or equal, inequality, equality)a | NA |
|`x is y, x is not y` | Identity tests | NA |
|`x in y, x not in y` | Membership tests | NA |
|`not x` | Boolean NOT | NA | 
|`x and y` | Boolean AND | L | 
|`x or y` | Boolean OR | L | 
|`x if expr else y` | Ternary operator | NA |
|`lambda arg,...: expr` | Anonymous simple function | NA |

@@

NumPy, short for Numerical Python, is one of the most important foundational packages for numerical computing in Python. Numpy works with array from 1-n dimensional.
